### 2024-06-07 Thesis.tex
wording

\textit{Функтором} между категориями $A$ и~$B$ называется упорядоченная пара $T = (T_1, T_2)$,
где $T_1$~— функция $\mathrm{Ob}(A) \rightarrow \mathrm{Ob}(B)$, а~$T_2$~— $\mathrm{Arr}(A) \rightarrow \mathrm{Arr}(B)$,
такая, что для~всяких объектов $a, b \in \mathrm{Ob}(A)$ и~стрелки $f \in \mathrm{hom}_C(a, b)$ выполняются
следующие условия:
\begin{enumerate}
    \item $T_2(f) \in \mathrm{hom}_C(T_1(a), T_1(b))$.
    \item $T_2(\mathrm{id}(a)) = \mathrm{id}(T_1(a))$.
    \item $T_2(g \circ f) = T_2(g) \circ T_2(f)$.
\end{enumerate}

>>>>

\textit{Функтором} между категориями $A$ и~$B$ называется упорядоченная пара $T = (T_1, T_2)$,
где $T_1$~— функция $\mathrm{Ob}(A) \rightarrow \mathrm{Ob}(B)$, а~$T_2$~— $\mathrm{Arr}(A) \rightarrow \mathrm{Arr}(B)$,
такая, что для~всяких объектов $a, b, c \in \mathrm{Ob}(A)$ и~стрелок $f \in \mathrm{hom}_C(a, b)$ и~$g \in \mathrm{hom}_C(b, c)$ выполняются
следующие условия:
\begin{enumerate}
    \item $T_2(f) \in \mathrm{hom}_C(T_1(a), T_1(b))$.
    \item $T_2(\mathrm{id}(a)) = \mathrm{id}(T_1(a))$.
    \item $T_2(g \circ f) = T_2(g) \circ T_2(f)$.
\end{enumerate}
